# Dataset Creation

```{r message=FALSE}
library(knitr)
library(PKPDmisc)
library(tidyverse)
library(vancomycin)
library(mrgsolve)
```

```{r}
source("../scripts/generate_demographics.R")
```

```{r}
models <- source("../models/models.R")$value
```

## Generate data for mrgsolve

start with a baseline of having 100 individuals worth of data, can scale to 
different amounts of individuals later

```{r}
set.seed(1234567)
NIDS <- 100
```

```{r}
demogs <- generate_demographics(NIDS) %>% mutate(ID = 1:nrow(.), 
                                                 PMA = PMA/7 # in weeks for stockmann model
                                                 )
```

```{r}
for_dosing <- demogs %>% 
                  mutate(
                      CMT = 1, 
                      EVID = 1,
                      TIME = 0
                  ) %>% select(ID, everything())
```


```{r }
all_dosing <- for_dosing %>% group_by(ID) %>%
    nest() %>%
    mutate(dose = map(data, ~ dosing_6bin_pna_wt(.$AGE, .$WT))
           ) %>% unnest() 
```

Dose for 8 days
```{r}
all_dosing <- all_dosing %>% 
  mutate(addl = 24/II*8) 
```

```{r}
kable(head(all_dosing))
```
```{r}
vanc_stockmann <- models$use("vanc_stockmann")
```

Normalize column capitalizations to make mrgsolve happy

```{r}
mrg_data <- bind_cols(
  all_dosing %>% select(ID),
  all_dosing %>% select(everything(), -ID) %>% lowercase_names()
  ) %>% mutate(amt = dose)
```

```{r}
raw_sim <- vanc_stockmann %>% data_set(mrg_data) %>% mrgsim(end = 10*24, delta = 2) %>%
  as.data.frame %>% as_data_frame %>% capitalize_names()
```

### Check distribution of trough values at SS
```{r}
peak_trough <- raw_sim %>% filter(between(TIME, 150, 200)) %>%
  select(ID, TIME, CP, DV) %>%
  gather(obs, value, CP, DV) %>%
  group_by(ID, obs) %>%
  summarize(ctrough = min(value),
            cmax = max(value))
```

Peak and trough values are representative of real observations
```{r}
peak_trough %>%
  gather(sample, value, ctrough, cmax) %>%
  ggplot(aes(x = value)) + 
  geom_density(aes(fill = obs), alpha = 0.6) +
  facet_wrap(~sample, scales = "free") + theme_bw() +
  base_theme()
```


* take simulated values and prepare for nonmem estimation

```{r}
from_sim <- raw_sim %>% 
  distinct(ID, TIME, DV)

from_orig <-  mrg_data %>% 
  capitalize_names() %>% 
  select(
    ID,
    TIME,
    WT,
    CRE,
    AGE,
    PMA, 
    HT,
    SEX,
    CMT,
    DOSE,
    II,
    ADDL
  )
```


```{r }
data_for_nonmem <- left_join(from_sim, from_orig) %>% 
  group_by(ID) %>%
  fill(WT:CMT) %>%
  mutate(
    EVID = ifelse(DV == 0, 1, 0)
  ) %>% 
  ## don't need to go too far after final dose for estimation purposes
  ## also don't n
  filter(TIME < 216) %>% 
  ## don't need 0 concentration time point as not realistic
  distinct(ID, TIME, .keep_all = TRUE)
```

### write data for nonmem

```{r}
write_nonmem(data_for_nonmem, "../modeling/mdata/rich_100.csv")
```

```{r cache = FALSE}
devtools::session_info()
```
